Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}). 
    % The layout is similar to Figure \ref{fig:abundance-evolution-yields}. 
    Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius. A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel. The black curve plots the ISM abundance at $R_{\rm gal}=8\kpc$ over time. The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin. Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$. {\bf Key takeaway:} Models with pre-enriched infall (c) or a higher thick-to-thin disk ratio (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}
    \label{fig:abundance-evolution-params}
\end{figure*}

@@

We next attempt to mitigate the dilution and late-time evolution problems for the empirical (\yZ{1}) yield scale. 
The remaining columns of Figure \ref{fig:abundance-evolution-params} show the effect of varying several parameters for the \yZ{1} model: (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the metallicity of the infalling gas $\mathXH_{\rm CGM}$, and (d) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$.

@@

Next, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk. Column (c) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population. Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies. The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced since the accreting gas is less chemically different from the ISM, diminishing the effects of dilution. The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity---an effect which can be compensated by a slightly increased value of $\eta$. This model also narrows the [O/Fe] distribution of mono-age populations (almost all the model stars fall within the $1\sigma$ band of the data), which could be compensated for by stronger radial migration.

Finally, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger that the fiducial value, $f_\Sigma(R_\odot)=0.5$. This choice places the ratio higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}). Column (d) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase. The model produces the best agreement with the observed age--[Fe/H] relation (second row). However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting a trend much flatter than observed, underpredicting [O/Fe] by $\sim0.1$ dex in the $\sim6-10\Gyr$ age range.

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations predicted by multi-zone models at the \yZ{1} yield scale (see Table \ref{tab:yields}). 
    % The layout is similar to Figure \ref{fig:abundance-evolution-yields}. 
    Each point represents a stellar population drawn from the Solar neighborhood near the midplane ($7\leq R_{\rm gal}\leq 9\kpc$, $0\leq |z| \leq 0.5\kpc$) and is color-coded by its birth radius. A Gaussian scatter is applied to each point according to the median age and abundance uncertainties in Table \ref{tab:uncertainties}. For visual clarity, we plot only a random mass-weighted sample of \num{10000} points in each panel. The black curve plots the ISM abundance at $R_{\rm gal}=8\kpc$ over time. The red line segments plot the median abundance for APOGEE stars in {2 Gyr}-wide age bins, and the shaded regions represent the 16th--84th percentiles in each bin. Age estimates for APOGEE stars come from \citet{leung_variational_2023}.
    Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\kpc$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\kpc$; {\bf (c)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.5$; and {\bf (d)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$. {\bf Key takeaway:} Models with a higher thick-to-thin disk ratio (c) or pre-enriched infall (d) reduce the magnitude of the ISM dilution, but neither completely match the observed age--metallicity relation.}
    \label{fig:abundance-evolution-params}
\end{figure*}

@@

We next attempt to mitigate the dilution and late-time evolution problems for the empirical (\yZ{1}) yield scale. 
The remaining columns of Figure \ref{fig:abundance-evolution-params} show the effect of varying several parameters for the \yZ{1} model: (b) the strength of radial migration $\sigma_{\rm RM8}$, (c) the local thick-to-thin disk density ratio $f_\Sigma(R_\odot)$, and (d) the metallicity of the infalling gas $\mathXH_{\rm CGM}$.

@@

Next, we explore a model where the local thick-to-thin disk surface density ratio is $\sim4$ times larger that the fiducial value, $f_\Sigma(R_\odot)=0.5$. This choice places the ratio higher than most of the constraints from population counts or GCE models (see Section \ref{sec:sfh}). Column (c) of Figure \ref{fig:abundance-evolution-params} shows that requiring a more massive thick disk can reduce the dilution and recent evolution of the ISM, similar to the pre-enriched infall, because more of the gas disk is built up during the first infall phase. The model produces the best agreement with the observed age--[Fe/H] relation (second row). However, agreement with the observed age--[O/Fe] relation is poor, with the model predicting a trend much flatter than observed, underpredicting [O/Fe] by $\sim0.1$ dex in the $\sim6-10\Gyr$ age range.

Finally, we investigate a model where the infalling gas is enriched to a metallicity $\mathOH=\mathFeH={\rm [X/H]}_{\rm CGM}$ before accreting onto the disk. Column (d) of Figure \ref{fig:abundance-evolution-params} shows results for the case where ${\rm [X/H]}_{\rm CGM}=-0.5$, the highest metallicity allowed by the local low-$\alpha$ population. Pre-enriched infall at this level mitigates but does not completely solve the two discrepancies. The dilution effect of the second infall is reduced to the $\sim0.3$-dex level as the gas which replenishes the Galaxy's reservoir is no longer pristine; however, the width of the stellar abundance distribution at any given age is also reduced since the accreting gas is less chemically different from the ISM, diminishing the effects of dilution. The late-time gas abundance evolution is similar to the fiducial model, but it ends at slightly super-Solar metallicity---an effect which can be compensated by a slightly increased value of $\eta$. This model also narrows the [O/Fe] distribution of mono-age populations (almost all the model stars fall within the $1\sigma$ band of the data), which could be compensated for by stronger radial migration.
